The LHC as a Neutrino-Ion Collider

### 2023-11-23 referee/referee-reply.tex

  \item The flux and the neutrino DIS cross-section have very different kinematic dependences.
    %
    The incoming nuetrino flux is mostly fixed from the $(E_\nu, y_\nu)$ dependence of the event rates,
    while the PDFs in the DIS cross-section are fixed by the $(x,Q^2)$ dependence.
    %
    By measuring event rates differentially in the three kinematic variables $(E_\nu, x,Q^2)$, and also
    accessing the $y_\nu$ dependence of the incoming neutrinos, one can efficiency disentangle the
    fluxes from the DIS cross-section.
    %
    Of course, one needs to explicitely demonstrate this via a dedicated analysis, but there
    is no conceptual reason preventing us from this goal.

   \end{itemize}

We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.

  "%
As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
%
If the spread of various generators' predictions was taken as a means of flux uncertainty, corresponding to a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum, this would be a significant systematic if left unresolved. However, it is noteworthy that many existing predictions are yet to be tuned for the purposes of experiments such as those planned for the FPF. Nevertheless, there are projections of FPF measurements which would reduce this uncertainty to the sub-percent level already in the context of the contemporary predictions, based on parametrizing their expected correlations~\cite{Kling:2023tgr}, as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
%
However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
%
In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
%
To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
%
With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits. Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future. The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
%"

### 2023-11-23 journal_sub/sec-dis-pseudodata.tex
minor typo
Modifying statement about flux uncertainties in referee reply and journal sub

%
As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
%
The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic. Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
%
However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
%
In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
%
To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
%
With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits. Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future. The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
%

>>>>

%
As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
%
If the spread of various generators' predictions was taken as a means of flux uncertainty, corresponding to a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum, this would be a significant systematic if left unresolved. However, it is noteworthy that many existing predictions are yet to be tuned for the purposes of experiments such as those planned for the FPF. Nevertheless, there are projections of FPF measurements which would reduce this uncertainty to the sub-percent level already in the context of the contemporary predictions, based on parametrizing their expected correlations~\cite{Kling:2023tgr}, as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
%
However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
%
In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
%
To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
%
With this assumption, we will show that Run 3 measurements will not be sufficient to impact PDF fits. Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future. The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
%
